\TITLE

### 2010-10-05 roadmap/plfs_roadmap.tex
git-svn-id: https://plfs.svn.sourceforge.net/svnroot/plfs/doc@346 979fb63a-54b4-4514-8d67-9ab8ea1b59df

\documentclass[10pt]{article}
\usepackage{fullpage}
\usepackage[pdftex]{graphics}
\usepackage{enumitem}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{alltt}
\setlist{noitemsep,topsep=0pt}
\setitemize{noitemsep,topsep=0pt}
\setenumerate{noitemsep,topsep=0pt}

@@

Figures~\ref{fig-conf}~and~\ref{fig-mapping} show how the mapping function
can be defined such that the same logical path will be resolved to the same
physical path on the \upfs.

@@

\begin{figure}[t]
\centering
\begin{tabular}{ p{3in} p{3in}}
\input{config.tex}
&
\input{admin.tex}
\\
\centering a) Configuration File & b) Administrator Script 
\end{tabular}
\mycaption{fig-conf}{Shared Mappings.}{On the left is an example \plfsrc\
file listing various parameters used to control the behavior within
the PLFS library.  Of interest here is how the mapping works to find a physical
location from a logical path.  The hashing function itself works by turning
the username into the uid and then taking the modulus of the uid and the
number of backends and then using that result as an index into the backend
array.  Note that the complexity of the hashing algorithm will really just
exist in the PLFS library but is shown here for the sake of expediency.  
Notice also that this method distributes each user's metadata workload 
to a different metadata server.  Of course, the entire metadata workload
for each individual user is isolated on a single metadata server.  We will
fix this in Version~2.
The right shows the script that an administrator
can use to setup the necessary directories.  The \$user\_list is defined to
be all users during initial creation and then set to be just a single user
when a new user is added.}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics{mapping.png}
\mycaption{fig-mapping}{Path Resolution in Shared Mappings.}{This figure
shows how the same logical path resolves in both \fuse\ and \adio\ to the
same path on the \upfs.  We assume that the \plfsrc\ used is that shown
in Figure~\ref{fig-conf}.}
\end{figure}

@@

\version{1}{Version 1 will have both the \fuse\ and \adio\ layers and a mapping
within the library layer will hide {\store}s from the users.  
Path resolution in both \fuse\ and \adio\ will share the same mapping such
that the same logical path presented to both will resolve to the same
physical path on the \upfs.
Each user's metadata workload will be isolated on one of a set of metadata
servers such that simultaneous workloads from multiple users will be spread
across multiple metadata servers.
}

@@

>>>>

\documentclass[10pt]{article}
\usepackage{fullpage}

\usepackage{enumitem}
\setlist{noitemsep,topsep=0pt}
\setitemize{noitemsep,topsep=0pt}
\setenumerate{noitemsep,topsep=0pt}

@@

However, one problem is that we can no longer depend on symbolic links to
spread users across volumes.  We can either put all {\store}s on a single
volume or we can put a mapping entry into \plfsrc\ for every user
(\eg\ \Path{/plfs/ben} maps to \Path{/panfs/scratch/vol5/ben/.plfs\_store}).
This might be a maintenance problem however as every time a new user is
added, every \plfsrc\ file will need to be updated.  I don't know
the administrative cost of this.

@@

@@

\version{1}{Version 1 will have both the \fuse\ and \adio\ layers and a mapping
within the library layer will hide {\store}s from the users.  With a simple
map file, all \plfs\ metadata for all users will go to a single PanFS director.
With a more complicated map, each user's metadata workload will go to different
directors.}

\policyq{Use a simple map and no metadata distribution or a complicated map
which spreads metadata workloads across PanFS directors?  Or skip Version 1
in favor of Version 2?}

@@

\subsection{Archive Workloads}

Gary Grider did a bunch of measurements on an HB machine and sent email on
August 3, 2010 about this.  The archive workload consists of a small number of
processes running on a small number of nodes reading a file in 500 MB strides.
When the file was created with a large number of writers, the time to open it
for reads (\ie\ the time to aggregate the index chunks into a global offset
lookup table) becomes large.  We added multi-threading to deal with this and
it helps but we anticipate that for Cielo-scale machines, these thread pools
will be insufficient and we'll need to solve this with index squashing.  Also,
the read bandwidth itself is OK for files created with 500K writes but runs
slowly for files created with 50K writes.  Specifically, it reads at about
a third of the bandwidth that files can be read directly from Panasas.  We
don't know what to do about this at the current time but this doesn't need
to be solved for Roadrunner and may not prove to be a problem even for Cielo.
